% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Colors: emerald, skyblue, red, pink, orange nephritis, concrete, darknight
\colorlet{default}{red}
% Uncomment if you would like to specify your own color
% \definecolor{default}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with default color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./images/fraguinha.png}

\name{João}{Fraga}
\position{Software Engineer}
\address{Rua do Amial 720 Apartment 1.8\\4200-055 Porto\\Portugal}

\mobile{(+351) 934 686 671}
\email{joao@fraguinha.com}
\homepage{fraguinha.com}
\github{fraguinha}
% \gitlab{fraguinha}
% \extrainfo{extra information}

% \quote{Emphasis phrase}

% The company being applied to
\company{Wellhub}
% The role
\role{Senior Software Engineer}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The recipient information
\recipientname{Recruitment Team}
\recipientaddress{Wellhub}

\lettertitle{Job Application for}
\letteropening{Dear Recruitment Team,}
\letterclosing{Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}

\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {João Fraga~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

\begin{cvletter}

I am excited to apply for the \makerole{} position and contribute to your innovative team.

\lettersection{About Me}

I am a software engineer with a proven record of delivering high-impact solutions that drive measurable improvements.
At my current role, I’ve been consistently promoted, reflecting both my technical expertise and leadership growth.
I have a strong track record in architecting scalable applications, with knowledge of SQL/NoSQL databases, containerization (Docker, Kubernetes), and designing robust RESTful APIs.
My background in competitive programming enhances my approach to data structures and complexity analysis, ensuring reliable and efficient solutions.
I’m excited to bring my experience to new challenges.

\lettersection{Why \makecompany{}}

I am inspired by \makecompany{}’s mission to build a flexible, scalable platform supporting millions globally.
The challenge of designing systems that balance high availability with the adaptability for evolving commercial models is a perfect fit for my experience in scalable architectures and cloud infrastructure.
I look forward to contributing to \makecompany{}'s vision and technical goals.

\lettersection{Why me}

With my experience in optimizing high-availability systems, leading scalable application architecture design, and my success in a fin-tech environment handling millions of daily transactions, I am confident I am a strong fit for the \makerole{} role at \makecompany{}.
I am excited about the opportunity to bring my skills to the team and help tackle meaningful technical challenges that align
with the company’s mission.

\end{cvletter}

\makeletterclosing

\end{document}
